\tool

### 2017-11-30 paper/paper.tex
Starting related work section

>>>>

Our work builds on previous research studying the lack of tool adoption by software engineers, methods for improving tool discovery, and existing approaches for automated tool recommendations.

Previous research has explored reasons why software engineers don't use helpful tools. Murphy-Hill and colleagues studied developers to uncover why programmers don't use refactoring tools for maintaining software~\cite{MurphyHillWhyRefactoringTools}. Johnson et al gathered data from software engineers to determine their perspective on static analysis tools and reasons for underuse~\cite{JohnsonStaticAnalysis}.
